master thesis

### 2018-03-22 Paper - Latex/Paper - Skizze - v4.tex
Paper - Pagenumbering, serifenlose Schrift
Paper - rearrange Introduction; refine OTL & GloBI

\begin{document}
  % Titelseite
  \begin{titlepage}
    \pagestyle{empty}
  	\begin{center}
      {\Large Freie Universität Berlin} \\
    	\begin{Huge}
      	Fachbereich Mathematik und Informatik \\
      	\vspace{3mm}
    	\end{Huge}
    	\vspace{2cm}
    	\begin{Large}
        \textbf{An analysis of maximum parsimony algorithms to predict parasitism in Eukaryota} \\
        \vspace{3mm}
        using a large multifurcated phylogenetic synthesis tree \\
    	\end{Large}
      \vspace{3cm}
      \textbf{Eingereicht am:} \\
      3.4.2018 \\
    	\vspace{2cm}
    	Lydia Buntrock \\
      E-Mail: info@irallia.de \\
     	\vspace{3cm}
      \textbf{Betreuer:} \\
      Dr. Bernhard Y. Renard \\
      \& \\
      Prof. Dr. rer. nat. Emanuel Heitlinger \\      
  	\end{center}
  	\clearpage
  \end{titlepage}

@@

\tableofcontents
\clearpage

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Introduction}
  This paper is about the analysis of ancestral state reconstruction algorithms for non-binary trees, 
    applied to the currently largest phylogenetic synthesis tree of Open Tree Of Life (OTL)
    \cite{Hinchliff2015}, with the application of prediciton of parasitism. \\
  % \todo{Or:} The aim of this paper is the application of maximum parsiomony algorithms to non-binary 
  %   trees and very large datasets. In particular, the example 'Origins of Parasitism' throughout the 
  %   Eukaryota Tree of Life. \\

  We will test the existing maximum parsimony algorithms Fitch \cite{Fitch1971} and Sankoff 
    \cite{Sankoff1975} for this task and estimate their predictive power. The present tree structure 
    of OTL is not binary. A tree is binary (or bifurcated), when each node has at most two children 
    otherwise it is multifurcated \cite{Felsenstein2003}. \\
  % \anmerkungstext{auch hier kannst du multiifurcated direkt erklären: that is it each not has 
    % multiple (n >= 3) children (Thilo)}
  Maximum parsimony methods are developed for phylogenies, which are usually depicted as binary trees.
    Parsimonious in phylogeny refers to favoring the tree that needs the least evolutionary change 
    to explain the observed data. In our case, it is about the change of states 'is free-living' or 
    'is parasitic'. \\
    % Parsimonious in this context means to minimize the number of transitions between species states 
    % (free-living or parasitic). 
  The Sankoff method is implemented by Louca et al. for the non-binary case and is available as an R 
    package called \textit{Castor} \cite{Louca2017}. In addition, we have implemented the Fitch 
    method and adapted it for multifurcated trees. \\% to make it usable and comparable for our current problem.
  This achieves that we can predict ancestral states and unknown states of living species for large 
    non-binary relatives trees. \\

  For about 50 years, people have been working on ancestral state reconstruction. The first paper 
    is by Camin and Sokal, who in 1965 were working on algorithms for discrete-state data 
    \cite{Camin1965}. Different methods have been developed and the question is which method is the 
    most suitable for the problem at hand: The ancestral state reconstruction for a huge 
    multifurcated tree with \colorbox{red}{binary/two discrete} states. \\
  \anmerkungstext{hier mehr dazu? Likelihood vs parsiomony... das befindet sich momentan im Methoden 
    Teil: Ancestral state reconstruction methods} \\
  % Royer-Carenzi et al. distinguishes two major classes of ancestral state reconstruction methods: \\
  %   The first is to explain the current state with the least number of state changes between an 
  %     ancestor and his child, this is called parsimonious. \\
  %   The other class she presents involves modeling the character evolution as a stochastic process and 
  %     using the likelihoods to compute the possible ancestral character states. This is generally done 
  %     with a continuous time Markov model \cite{RoyerCarenzi2013}. \\

  % The first methods were only brute force \todo{Quelle, siehe Fitch: Camin and Sokal 1965}. 
  %   Next came a set of parsimony algorithms such as: Fitch-parsimony \cite{Fitch1971}, 
  %   Wagner-parsimony \cite{Swofford1987} ... \todo{weitere?}. \\
  %   With more and more data, there is now the possibility to use more information to calculate the 
  %   probabilities of the ancestral states. In addition to the states of the leafs, algorithms could 
  %   also use branch lengths. The likelihood based algorithms came more in interest. \\

  % We have decided to consider only parsimony algorithms since we have no information on branch 
  % lengths and no other additional information like different transition probabilities of our states.

  For this purpose, various studied methods and their advantages and disadvantages will be compared. \\
  These algorithms were developed especially for the binary problem, since one has considered much 
    smaller subtrees, of which one knows all the splits. \\
  By developing a whole of an entire tree of life, the problem arises that it is by no means binary. \\

  For these large phylogenetic synthesis trees, however, ancestral state reconstruction has so far 
    only been done for Bacteria and Archaea for binary traits by Goberna and Verdú \cite{Goberna2015}.
    However, this differs from eukaryotes in the sense that complex traits such as parasitism depend
    on more than one gene. \\

@@

  At this point a few words to the term parasitic. There are different definitions. Since we use 
    GloBI to classify species, we use their definition of parasitism. Again, in GloBi, Ontobee 
    definitions are used \cite{Xiang2011}.
  The interaction \textit{has parasite} is defined as: "An interaction relationship between two 
    organisms living together in more or less intimate association in a relationship in which 
    association is disadvantageous or destructive to one of the organisms." \cite{...}. This 
    definition includes: ecto- and endoparasites, parasitoids, kleptoparasites and pathogenes.
  \todotext{Mungall, C., (2017). Definition for the interaction-term: "parasitised by; has parasite" 
  ob ontobee.org. Last checked: 24.07.2017 at 
  \hyperlink{ontobee.org/ontology/RO?iri=http://purl.obolibrary.org/obo/RO_0002445}
  {ontobee.org/ontology/...}} \\

  The objectives of this work are the following points: (1) Find a suitable ancestral state 
    reconstruction method. (2) Perform reconstructing on the Eucaryotic synthesis tree of OTL. \\
  The goal of Point 1 is to evaluate the possible methods based on a simulation of our data 
    situation. \\
  The one by Louca et al. implemented Sankoff algorithm is the best in our comparisons. Therefore, 
    point 2 consists of reconstructing the ancestral states and predicting the unknown leaf states. 
    And then perform an evaluation of the results.

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Methods}
  As initiated, in this paper, a maximum parsimony algorithm is applied to the whole tree of life to 
    obtain an ancestral state reconstruction of free-living versus parasite states. \\
  So far, these reconstructions have been made mainly on binary trees with better data availability. 
    Therefore, a simulation is first performed to evaluate existing algorithms and decide how they 
    may be adapted to our given problem. This is to perform the ancestral state reconstruction for a 
    multifurcated (non-binary) tree using binary states. \\
  Accordingly, in addition to the necessary data sets (GloBI, OTL), the chosen algorithm and the 
    evaluation of its results, this chapter also deals with the previously performed simulation and 
    the evaluation of the various algorithms and their parameters. \\
  Figure \ref{fig:workflow} briefly outlines these relationships.
  \begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{Figures/Workflow-overview.png}
    \caption{Workflow \\
      The resulting procedure is as follows: \\
      (1) Retrieve phylogenentic tree data as input for the tree (OTL) and the state information (GloBI).
      (2) Get metadata of these for a realisitc the simulation of the maximum parsimony algorithms (Fitch \& Sankoff).
      (3) Build and run the simulation.
      (4) Evaluation of parameters for the simulation and the ancestral state reconstruction of the real tree.
      (5) Evaluate the accuracy of developed algorithms and choose the best.
      (6) Run the resulted algorithm on the original data.
      (7) Evalute and interprete results. %$\rightarrow$ Origins etc...
    }
    \label{fig:workflow}
  \end{figure}

  \todo{In den einzelnen Abschnitten Teile von dem großen Workflow verwenden?: \ref{fig:BigWorkflow}}

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Description of data sets}
    For \colorbox{red}{our} research two types of data are required: a tree and information about the 
      states. \\
    For the tree \colorbox{red}{we} decided to use Open Tree of Life (OTL) \cite{Hinchliff2015}. \\
    For the state information, \colorbox{red}{we} decided to use the Global biotic interaction 
      database (GloBI) \cite{Poelen2014}.

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{OTL}
      For \colorbox{red}{our} project a large database for phylogenetic trees and also for a taxonomic 
        tree is needed. Since an ancestral state reconstruction algorithm is applied to the phylogenetic 
        tree, and for the assessment and other properties the taxonomy provides much more information. \\
      OTL gives a synthesis of phylogenetic trees (currently 819 trees) and a taxonomic tree. OTL also 
        includes the large phylogenetic database TreeBASE \cite{Hinchliff2015}. \\
      \todo{Das steht auf der Website nicht in dem Paper...} \\
      For phylogenetic data, there are at least five big data collections, namely:
      \begin{itemize}
        \item ITIS (Integrated Taxonomic Information System) \cite{ITIS}
        \item NCBI (National Center for Biotechnology Information) \cite{NCBI1988}
        \item WORMS (World Register of Marine Species) \cite{WoRMS2018}
        \item GBIF (Global Biodiversity Information Facility) \cite{GBIF}
        \item OTT (OpenTreeOfLife-Taxonomy) \cite{Hinchliff2015}
      \end{itemize}
      \todo{In die discussion?:} \\
      ITIS is only a small set of 100~\% confirmed and named species. GBIF is not composed with the help 
        of phylogeny, the same is valid for the NCBI taxonomy. The WORMS taxonomy is a way too small 
        dataset of mostly marine species. \\
      Here the taxonomy from OTL is used because it is including most of the known taxonomies and is 
        synthesised by preffering taxonomies that match with available phylogenetic data. Furthermore 
        the team from OTL preferre a maximum number of species \cite{Hinchliff2015}. This is resulting 
        in somekind of hybrid between taxonomy and phylogeny. \anmerkungstext{Wie genau ist das ein 
        Hybrid? Genauer beschreiben, was Du damit meinst... (Thilo)} \\

@@

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{GloBI}
      \todotext{Marius:} "There aren't many big active interaction databases out there, most of them are 
        offline or outdated. For example: IWDB (Interaction Web Database) \cite{IWDB2003}, Webs on the 
        Web \cite{WOW2004}, Animal Diversity Web \cite{Myers2003} and ecoweb \cite{Cohen2010}. GloBI is 
        including most of the known ones and is still growing actively \cite{Poelen2014}. So the 
        question which interaction database could be used was answered rather quickly." \\

      This database consists of entries of the form: species A (source) interacts with B (target). \\
      A number of interactions have been identified\footnote{\hyperlink{
        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java
        }{https://github.com/jhpoelen/eol-globi-data/.../InteractType.java}}
        ,including those that the species source or target has become a parasite or a free-living 
        species from the biological perspective. These are the following:
      \begin{itemize}
        \item free-living source: preysOn, eats, flowersVisitedBy, hasPathogen, pollinatedBy, 
          hasParasite, hostOf
        \item free-living target: preyedUponBy, parasiteOf, visitsFlowersOf, pathogenOf, hasHost
        \item parasite source: parasiteOf, pathogenOf
        \item parasite target: hasParasite, hasPathogen
      \end{itemize}
      Of these interactions, e.g. species A parasitize species B, the state of the species is 
        determined, here is species A parasitic and species B free-living. The case a parasite 
        conquers (parasitizes) another parasite yields conflicting states for the second species. 
        This is solved by preferring parasitic. \\
      Two lists are formed: parasites and free-livings, and the source or targets of an interaction
        are added to these.

@@

@@

        Input: A rooted, binary tree, with state informations in the leaf nodes. Each node is depicted as 
          a set of states. There are only two states in this paper, free-living (FL) and parasitic (P). 
          Internal nodes have three sets, which are empty at the beginning, excluding the root node, it 
          has only one. Leaf nodes have their state as a set (eg \{FL\} or \{P\}, unknown leaf nodes the 
          union of all possible states (\{FL, P\}). \\
        The algorithm traverses three times trough the tree and fills these sets. \\
        In each step, two sets are considered and their intersect formed. There are two cases:
        \begin{enumerate}
          \item The intersection is not empty and corresponds to the new set.
          \item The intersection is empty. $\rightarrow$ Build the union of these sets as new set.
        \end{enumerate}

>>>>

\begin{document}
  % Titelseite
  \begin{titlepage}
    \pagestyle{empty}
  	\begin{center}
      {\Large Freie Universität Berlin} \\
    	\begin{Huge}
      	Fachbereich Mathematik und Informatik \\
      	\vspace{3mm}
    	\end{Huge}
    	\vspace{2cm}
    	\begin{Large}
        \textbf{An analysis of maximum parsimony algorithms to predict parasitism in Eukaryota} \\
        \vspace{3mm}
        using a large multifurcated phylogenetic synthesis tree \\
    	\end{Large}
      \vspace{3cm}
      \textbf{Eingereicht am:} \\
      3.4.2018 \\
    	\vspace{2cm}
    	Lydia Buntrock \\
      E-Mail: info@irallia.de \\
     	\vspace{3cm}
      \textbf{Betreuer:} \\
      Dr. Bernhard Y. Renard \\
      \& \\
      Prof. Dr. rer. nat. Emanuel Heitlinger \\      
  	\end{center}
    \clearpage
    \pagenumbering{Roman}
  \end{titlepage}

@@

\tableofcontents
\clearpage
\pagenumbering{arabic}

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Introduction}
  This thesis is about the analysis of ancestral state reconstruction algorithms for non-binary 
    trees, applied to the currently largest phylogenetic synthesis tree of Open Tree of Life (OTL)
    \cite{Hinchliff2015}, with the application of prediciton of parasitism. \\

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %--------------------------------------------------------------------------------------------------- 
  \section{Motivation}
    The aim of this thesis is the application of maximum parsiomony algorithms to non-binary 
      trees and very large datasets. In particular, the example find the 'Origins of Parasitism' 
      throughout the Eukaryota Tree of Life. \\
    For these large phylogenetic synthesis trees, however, ancestral state reconstruction has so far 
      only been done for Bacteria and Archaea for binary traits by Goberna and Verdú \cite{Goberna2015}.
      However, this differs from eukaryotes in the sense that complex traits such as parasitism depend
      on more than one gene. \\
    \todo{Warum ist das relevant? Was könnte man dann tun?}

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %--------------------------------------------------------------------------------------------------- 
  \section{Background}
    For about 50 years, people have been working on ancestral state reconstruction. The first paper 
      is by Camin and Sokal, who in 1965 were working on algorithms for discrete-state data 
      \cite{Camin1965}. Different methods have been developed and the question is which method is the 
      most suitable for the problem at hand: The ancestral state reconstruction for a huge 
      multifurcated tree with \colorbox{red}{binary/two discrete} states. \\
    Royer-Carenzi et al. distinguishes two major classes of ancestral state reconstruction methods: \\
    The first is maximum parsimony: explain the current state with the least number of state changes 
      between the child and his ancestor. \\
    The other class she presents describes modeling the character evolution as a stochastic process and 
      using the likelihoods to compute the possible ancestral character states. This is generally done 
      with a continuous time Markov model \cite{RoyerCarenzi2013}. \\

    Parsimony methods are simple methods in which you can not include information such as branch 
      length (development time of the species). This is also their main point of criticism compared to 
      the more complex likelihood based models. Since there are no branch lengths or other information 
      available for the present relationship tree, and thus can not take advantage of the 
      other models, we decided in favor for parsimonious. \\

    We will test the existing maximum parsimony algorithms Fitch \cite{Fitch1971} and Sankoff 
      \cite{Sankoff1975} for this task and estimate their predictive power. The present tree structure 
      of OTL is not binary. A tree is multifurcated if each node has multiple ($n >= 3$) children 
      \cite{Felsenstein2003}. \\
    Maximum parsimony methods are developed for phylogenies, which are usually depicted as binary trees.
      Parsimonious in phylogeny refers to favoring the tree that needs the least evolutionary change 
      to explain the observed data. In our case, it is about the change of states 'is free-living' or 
      'is parasitic'. \\
      % Parsimonious in this context means to minimize the number of transitions between species states 
      % (free-living or parasitic). 
    The Sankoff method is implemented by Louca et al. for the non-binary case and is available as an R 
      package called \textit{Castor} \cite{Louca2017}. In addition, we have implemented the Fitch 
      method and adapted it for multifurcated trees. \\% to make it usable and comparable for our current problem.
    This achieves that we can predict ancestral states and unknown states of living species for large 
      non-binary relatives trees. \\

    % For this purpose, various studied methods and their advantages and disadvantages will be compared. \\
    % These algorithms were developed especially for the binary problem, since one has considered much 
    %   smaller subtrees, of which one knows all the splits. \\
    % By developing a whole of an entire tree of life, the problem arises that it is by no means binary. \\

@@

    At this point a few words to the term parasitic. There are different definitions. Since we use 
      GloBI to classify species, we use their definition of parasitism. Again, in GloBi, Ontobee 
      definitions are used \cite{Xiang2011}.
    The interaction \textit{has parasite} is defined as: "An interaction relationship between two 
      organisms living together in more or less intimate association in a relationship in which 
      association is disadvantageous or destructive to one of the organisms."\footnote{
        \hyperlink{http://www.ontobee.org/ontology/RO?iri=http://purl.obolibrary.org/obo/RO_0002445}
        {ontobee.org/ontology/RO?iri=http://purl.obolibrary.org/obo/RO\_000244}; Last checked: 22.03.2018.
      }. This definition includes: ecto- and endoparasites, parasitoids, kleptoparasites and pathogenes.

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %--------------------------------------------------------------------------------------------------- 
  \section{Structure of this work}
    The objectives of this work are the following points: (1) Find a suitable ancestral state 
      reconstruction method. (2) Perform reconstructing on the Eucaryotic synthesis tree of OTL. \\
    The goal of Point 1 is to evaluate the possible methods based on a simulation of our data 
      situation. \\
    The one by Louca et al. implemented Sankoff algorithm is the best in our comparisons. Therefore, 
      point 2 consists of reconstructing the ancestral states and predicting the unknown leaf states. 
      And then perform an evaluation of the results.

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter{Methods}
  As stated in the introduction, in this thesis, a maximum parsimony algorithm is applied to the 
    whole tree of life to obtain an ancestral state reconstruction of free-living versus parasite 
    states. \\
  So far, these reconstructions have been made mainly on binary trees with better data availability. 
    Therefore, a simulation is first performed to evaluate existing algorithms and decide how they 
    may be adapted to our given problem. This is to perform the ancestral state reconstruction for a 
    multifurcated (non-binary) tree using binary states. \\
  Accordingly, in addition to the necessary data sets (GloBI, OTL), the chosen algorithm and the 
    evaluation of its results, this chapter also deals with the previously performed simulation and 
    the evaluation of the various algorithms and their parameters. \\
  Figure \ref{fig:workflow} briefly outlines these relationships. A more detailed view of the 
    workflow can be found in the appendix \ref{fig:BigWorkflow}.
  \begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{Figures/Workflow-overview.png}
    \caption{The Workflow of the resulting procedure with the following steps: \\
      (1) Retrieve phylogenentic tree data as input for the tree (OTL) and the state information (GloBI).
      (2) Get metadata of these for a realisitc the simulation of the maximum parsimony algorithms (Fitch \& Sankoff).
      (3) Build and run the simulation.
      (4) Evaluation of parameters for the simulation and the ancestral state reconstruction of the real tree.
      (5) Evaluate the accuracy of developed algorithms and choose the best.
      (6) Run the resulted algorithm on the original data.
      (7) Evalute and interprete results. %$\rightarrow$ Origins etc...
    }
    \label{fig:workflow}
  \end{figure}

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Description of data sets}
    Two types of data are needed for an ancestral state reconstruction: a tree and information about 
      the states. \\
    For the Tree Open Tree of Life (OTL) is used \cite{Hinchliff2015} and for the state information 
      the Global Biotic Interaction database (GloBI) is taken \cite{Poelen2014}. \\
    % These are presented below.

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{OTL}
      For this project a large database for phylogenetic trees and also for a taxonomic tree is needed. 
        Since an ancestral state reconstruction algorithm is applied to the phylogenetic tree, and for 
        the assessment and other properties the taxonomy provides much more information. \\
      OTL gives a synthesis of phylogenetic trees (currently 819 trees) and a taxonomic tree\footnote{
          \hyperlink{https://tree.opentreeoflife.org/about/synthesis-release/v9.1}
          {https://tree.opentreeoflife.org/about/synthesis-release/v9.1}; Last checked: 22.03.2018.
        }. OTL also 
        includes the large phylogenetic database TreeBASE \cite{Hinchliff2015}. \\
      \todo{Das steht auf der Website nicht in dem Paper...} \\
      For phylogenetic data, there are at least five big data collections, namely:
      \begin{itemize}
        \item ITIS (Integrated Taxonomic Information System) \cite{ITIS}
        \item NCBI (National Center for Biotechnology Information) \cite{NCBI1988}
        \item WORMS (World Register of Marine Species) \cite{WoRMS2018}
        \item GBIF (Global Biodiversity Information Facility) \cite{GBIF}
        \item OTT (OpenTreeOfLife-Taxonomy) \cite{Hinchliff2015}
      \end{itemize}
      \todo{In die discussion?:} \\
      ITIS is only a small set of 100~\% confirmed and named species. GBIF is not composed with the help 
        of phylogeny, the same is valid for the NCBI taxonomy. The WORMS taxonomy is a way too small 
        dataset of mostly marine species. \\
      Here the taxonomy from OTL is used because it is including most of the known taxonomies and is 
        synthesised by preffering taxonomies that match with available phylogenetic data. Furthermore 
        the team from OTL preferre a maximum number of species \cite{Hinchliff2015}. This is resulting 
        in somekind of hybrid between taxonomy and phylogeny. \anmerkungstext{Wie genau ist das ein 
        Hybrid? Genauer beschreiben, was Du damit meinst... (Thilo)} \\

@@

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{GloBI}
      The most big interaction databases are offline or outdated. For example: IWDB (Interaction Web 
        Database) \cite{IWDB2003}, Webs on the Web \cite{WOW2004}, Animal Diversity Web \cite{Myers2003} 
        and ecoweb \cite{Cohen2010}. GloBI is including most of the known ones and is still growing 
        actively \cite{Poelen2014}. So the question was answered rather quickly which interaction 
        database could be used. \\

      This database consists of entries of the form: species A (source) interacts with B (target). \\
      A number of interactions have been identified\footnote{\hyperlink{
        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java
        }{https://github.com/jhpoelen/eol-globi-data/.../InteractType.java}}
        ,including those that the species source or target has become a parasite or a free-living 
        species from the biological perspective. These are the following:
      \begin{itemize}
        \item free-living source: preysOn, eats, flowersVisitedBy, hasPathogen, pollinatedBy, 
          hasParasite, hostOf
        \item free-living target: preyedUponBy, parasiteOf, visitsFlowersOf, pathogenOf, hasHost
        \item parasite source: parasiteOf, pathogenOf
        \item parasite target: hasParasite, hasPathogen
      \end{itemize}
      Of these interactions, e.g. species A parasitize species B, the state of the species is 
        determined, here is species A parasitic and species B free-living. The case a parasite 
        conquers (parasitizes) another parasite yields conflicting states for the second species. 
        This is solved by preferring parasitic. \\
      For each species known IDs are stored in GloBI. This includes OTT (the taxonomy of OTL). All 
        species that have stored an OTT id and have a matching interaction are formed into two lists: 
        parasites and free-livings.

@@

    % The first methods were only brute force \cite{Camin1965} 
    %   Next came a set of parsimony algorithms such as: Fitch-parsimony \cite{Fitch1971}, 
    %   Wagner-parsimony \cite{Swofford1987} ... \todo{weitere?}. \\
    %   With more and more data, there is now the possibility to use more information to calculate the 
    %   probabilities of the ancestral states. In addition to the states of the leafs, algorithms could 
    %   also use branch lengths. The likelihood based algorithms came more in interest. \\

@@

        Input: A rooted, binary tree, with state informations in the leaf nodes. Each node is depicted as 
          a set of states. There are only two states in this thesis, free-living (FL) and parasitic (P). 
          Internal nodes have three sets, which are empty at the beginning, excluding the root node, it 
          has only one. Leaf nodes have their state as a set (eg \{FL\} or \{P\}, unknown leaf nodes the 
          union of all possible states (\{FL, P\}). \\
        The algorithm traverses three times trough the tree and fills these sets. \\
        In each step, two sets are considered and their intersect formed. There are two cases:
        \begin{enumerate}
          \item The intersection is not empty and corresponds to the new set.
          \item The intersection is empty. $\rightarrow$ Build the union of these sets as new set.
        \end{enumerate}
